
\documentclass{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[9pt]{extsizes}
\usepackage[margin=.5in, a4paper]{geometry}

\input{glyphtounicode}



\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1



%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  \textbf{\Huge \scshape Omar Ahmed Elsayed} \\ \vspace{1pt}
  \small +201501179339 $|$ \href{mailto:omar@omarx.uk}{\underline{omar@omarx.uk}} $|$ \href{https://omarx.uk}{\underline{omarx.uk}}\\
  \smallskip
  \href{https://www.linkedin.com/in/omarahmed-oa/}{\underline{linkedin.com/in/omarahmed-oa}} $|$
  \href{https://github.com/OmarAhmed-A}{\underline{github.com/OmarAhmed-A}}
\end{center}


\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: VHDL, C, CPP, Python, JavaScript, SQL, C\#, Golang, Dart, Markdown, LaTeX} \\
        \textbf{Developer Tools}{: Git, SSH, Linux, Google Cloud Platform, VS Code, Visual Studio} \\
        \textbf{Libraries}{: SciKitLearn, pandas, NumPy, Matplotlib, TensorFlow: Keras}
        }}
\end{itemize}



%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://github.com/OmarAhmed-A/Hyper-Market-Manegment-Semester6}{\underline{\textbf{Hyper Market Management System}}} $|$ \emph{Java, MySQL, NetBeans, jBCrypt, FlatLaf}}{Jun 2023}
\resumeItemListStart
\resumeItem{Revolutionized market management with a comprehensive system for sales, purchases, and employee roles.}
\resumeItem{Implemented administrative, marketing, inventory management, sales, and user modules.}
\resumeItem{Used Java for backend development, NetBeans for GUI, and MySQL for the database.}
\resumeItem{Enhanced security with password management using jBCrypt and improved design using FlatLaf.}
\resumeItem{Packaged for easy installation using jpackage with an executable installer available in the releases.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/OmarAhmed-A/Nvidia-DLI-Intro-to-DeepLearning}{\underline{\textbf{Experiments in DL and TL}}} $|$ \emph{Python, TensorFlow: Keras, Deep Learning, Transfer Learning}}{Nov 2022}
\resumeItemListStart
\resumeItem{Created an 11 layer CNN to classify ASL hand signs.}
\resumeItem{Augmented training images to increase variety and prevent overfitting.}
\resumeItem{Generated news headlines using an LSTM model.}
\resumeItem{Prepared ImageNet for transfer learning and Retrained ImageNet to detect the presence of a specific dog in a photograph.}
\resumeItem{Fine-tuned hyperparameters to reach an accuracy of 97\%.}
\resumeItem{Retrained ImageNet to identify rotten fruits, Fine-tuned hyperparameters achieving 96\% accuracy.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/OmarAhmed-A/Final-Project-finding-donors}{\underline{\textbf{Finding Donors}}} $|$ \emph{Python, ScikitLearn, pandas, Numpy, Matplotlib}}{Jul 2022}
\resumeItemListStart
\resumeItem{Implemented and measured the performance of three supervised models}
\resumeItem{Cleaned and prepared the data for Machine Learning}
\resumeItem{Optimized final model using grid search reaching 87.04\% accuracy}
\resumeItemListEnd
\resumeProjectHeading
{\href{https://github.com/OmarAhmed-A/PortfolioWebsite}{\underline{\textbf{Portfolio website}}} $|$ \emph{Node.js, JavaScript, GCP, NGINX, GitHub API}}{Jun 2022}
\resumeItemListStart
\resumeItem{Developed a portfolio website using Node.js and JavaScript, building upon an open-source project}
\resumeItem{Hosted the website on GitHub Pages and utilized GCP and NGINX for deployment and server management}
\resumeItem{Integrated the GitHub API to automatically display my latest projects and repositories}
\resumeItem{Used the project as an opportunity to expand my skills in web development}
\resumeItem{Website accessible at \href{https://omarx.uk}{\underline{omarx.uk}}}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{ALX Data Science Course By ExploreAI (Tuition sponsored by Mastercard)}{Cairo, Egypt/Online}
{Comprehensive data science training covering analysis, modeling, Python, SQL, and cloud computing}{Apr. 2023 -- Aug. 2024}
\resumeSubheading
{Arab Academy for Science, Technology and Maritime Transport}{Cairo, Egypt}
{Bachelor of Science in Computer Engineering; Currently Achieved 126/180 Credit Hours}{Sep. 2020 -- May 2025}
\resumeSubheading
{NVIDIA Deep Learning Institute}{Online}
{Fundamentals of Deep Learning \href{https://courses.nvidia.com/certificates/5d58177d4fb040e2afbf8aca6deb30db/}{\underline{Certificate}}}{November 2022}
\resumeSubheading
{Udacity} {Online}
{Machine Learning Cross-Skilling Nanodegree \href{https://graduation.udacity.com/confirm/DU5NCRMP}{\underline{Certificate}}}{Jul 2022 -- Aug 2022}
\resumeSubheading
{Visa - Forage} {Online}
{Visa Token Service Technology Virtual Experience Program \href{https://forage-uploads-prod.s3.amazonaws.com/completion-certificates/Visa/8ebZgyZyLA6h5gyqt_Visa_CxSSnup6ZjYxTvK6e_1676647035163_completion_certificate.pdf}{\underline{Certificate}}}{Feb 2023}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Subject Matter Expert and Technical Support Agent}{June 2023 -- Dec 2023}
{Teleperformance Egypt (OFF-SHORE Account (NDA))}{Cairo, Egypt}
\resumeItemListStart
\resumeItem{Provided exceptional support to customers, resolving complex issues.}
\resumeItem{Assisted in training and onboarding new agents, ensuring they were equipped with the necessary knowledge and skills.}
\resumeItem{Demonstrated strong communication and interpersonal abilities while interacting with customers and team members.}
\resumeItem{Developed problem-solving and critical thinking skills by analyzing and troubleshooting technical challenges.}
\resumeItem{Exhibited adaptability and a willingness to learn, staying updated with the latest technologies and industry trends.}
\resumeItem{Strictly followed quality standards and procedures to deliver consistent and compliant service.}
\resumeItem{Handled sensitive customer data with utmost care, adhering to PCI compliance and data security protocols.}
\resumeItemListEnd

\resumeSubheading
{Embedded electronics Team member}{Sep 2022 -- Present}
{IEEE Aast Cairo Student Branch}{Cairo, Egypt}
\resumeItemListStart
\resumeItem{Volunteered to help organise IEEE Explore a Worldwide programming competition held at Aast for the Egypt Section.}
\resumeItem{Worked on research and development of a small maze-solving robot for micro-mouse competition.}
\resumeItem{Developed a Python Teaching program for IEEE Women in Engineering (WIE) to teach Python to high school students.}

\resumeItemListEnd

\resumeSubheading
{Machine Learning Engineer}{March 2023}
{Dell Hacktrick Hackathon}{Dell technologies, Cairo, Egypt}
\resumeItemListStart
\resumeItem{Collaborated in a team of six (\href{https://github.com/OmarAhmed-A/DigitalSquad}{\underline{DigitalSquad}}) to develop an intelligent agent for a maze problem using Deep Q-Networks algorithm.}
\resumeItem{Implemented DQN algorithm in TensorFlow and PyTorch, and created a central repository for the code.}
\resumeItem{Set up a cloud server on AWS EC2, and a Conda environment to reduce latency and ensure smooth code execution.}
\resumeItem{Provided assistance on the algorithmic approach, and developed a translation layer for standard RL algorithms to work with the non standard competition environment.}
\resumeItem{Ranked seventh out of 10 teams in the final phase, from 30 of 200 teams that signed up for phase one.}
\resumeItem{Won the award for best spirit team, and gained valuable experience in machine learning, teamwork, and problem-solving.}
\resumeItemListEnd





\resumeSubheading
{Entrepreneurs Team Member}{Oct 2020 -- Jan 2021}
{Enactus AAST}{Cairo, Egypt}
\resumeItemListStart
\resumeItem{Collaborated with team members to achieve target results from the UN SDGs.}
\resumeItem{Created research reports to document and communicate goals and accomplishments.}
\resumeItem{Identified issues, analyzed information, and provided solutions to problems in biweekly meetings.}
\resumeItemListEnd

\resumeSubHeadingListEnd



\end{document}